Design, Implementation, and Evaluation of Open Power Quality

### 2020-06-22 07-opq-mauka.tex
More updates to the pilot and OPQ view clarifications.

There are remaining challenges to creating a useful power quality sensor network. First, the data provided by OPQ Boxes is low-level, "primitive" data consisting of either features (i.e. frequency, voltage, THD, and transients) or waveform data. But what we actually want is actionable insights into grid stability. For example, we might want to know if a given anomalous data value is actually detrimental, or we might wnat to be able to predict when a power quality event might occur in the future based upon the recognition of cyclical events in the historical data.

@@

%\begin{tcolorbox}[colback=red!5!white,colframe=red!75!black,title=ANTHONY]
%Please review the following paragraphs for accuracy and quality.
%\end{tcolorbox}

>>>>

There are remaining challenges to creating a useful power quality sensor network. First, the data provided by OPQ Boxes is low-level, "primitive" data consisting of either features (i.e. frequency, voltage, THD, and transients) or waveform data. But what we actually want is actionable insights into grid stability. For example, we might want to know if a given anomalous data value is actually detrimental, or we might want to be able to predict when a power quality event might occur in the future based upon the recognition of cyclical events in the historical data.

@@

### 2020-06-22 08-opq-view.tex

The home page ``System Stats'' widget shows the number of items stored at each OPQ storage level. The right hand column shows items that have been stored all time (not including items that have been discarded due to TTL). Thus, the left column of system data shows items that have been saved by TTL from either events, incidents, or phenomena. The left column shows items that have been collected in a single day (not including items that have been discarded by TTL).

>>>>

The home page's ``System Stats'' widget shows the number of items stored at each OPQ storage level. The right hand column shows items that have been stored all time (not including items that have been discarded due to TTL). The left column shows items that have been collected in a single day (not including items that have been discarded by TTL).
